First steps in synthetic algebraic geometry

### 2017-03-16 snippets/qcoh.tex
Interpretation of the synthetic definition

\begin{thm}Let~$E \in \Zar(S)$ be an~$\affl$-algebra.
If~$E$ is quasicoherent, that is of
the form~$\E_0^\Zar$ for some quasicoherent~$\O_S$-module~$\E_0$,
then~$E$ is synthetically quasicoherent from the internal point of view of~$\Zar(S)$.
The converse holds in any of the following situations:
\begin{enumerate}
\item The site used to construct~$\Zar(S)$ is one of the parsimonious sites.
\item The base scheme~$S$ is concentrated (quasicompact and quasiseparated) and
the functor~$E$ maps directed limits of inverse systems of~$S$-schemes with
affine transition morphisms to colimits in~$\Set$.
\end{enumerate}
\end{thm}

>>>>

This definition has the following interpretation. The codomain of the displayed
canonical map is the set of all~$E$-valued functions on~$\Spec(A)$. Elements
of~$E \otimes_R A$ induce such functions; these induced functions can
reasonably be called ``algebraic''. In a synthetic context, there should be no
other~$E$-valued functions as these algebraic ones, and different algebraic
expressions should yield different functions. This is precisely what the
postulated bijectivity expresses.

\begin{thm}\label{thm:qcoh-big-char}
Let~$E \in \Zar(S)$ be an~$\affl$-module.
If~$E$ is quasicoherent, that is of
the form~$\E_0^\Zar$ for some quasicoherent~$\O_S$-module~$\E_0$,
then~$E$ is synthetically quasicoherent from the internal point of view of~$\Zar(S)$.
The converse holds in any of the following situations:
\begin{enumerate}
\item The site used to construct~$\Zar(S)$ is one of the parsimonious sites.
\item The base scheme~$S$ is concentrated (quasicompact and quasiseparated) and
the functor~$E$ maps directed limits of inverse systems of~$S$-schemes with
affine transition morphisms to colimits in~$\Set$.
\end{enumerate}
\end{thm}
